---
title: "Lab 10"
author: "Conner Smith"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(usethis)
library(janitor)
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
library(multicolor)
```

## Beepr beeps

Use the function `beep()` in the beepr package to make an audio alert when your code is done running.

```{r, eval = FALSE}
for (i in rev(seq(1:9999))) {
  print(paste(i, "bottles of beer on the wall"))
}

# beep(4)
```

## praise and cowsay

Packages built with a single purpose: to be kind and fun

```{r}
praise("${Exclamation}, ${EXCLAMATION}...${exclamation}!!!")

praise("Holy ${creating}, Batman - this code is ${ADJECTIVE}")

say(by = "hypnotoad", by_color = "rainbow")
```

Use cowsay::say() to make character say something 

`usethis::edit_r_profile()`

# Backend project into Github 

`usethis::use_git()`
`usethis::use_gitbub()`


## paletteer to access thousands of color palettes 

view(palettes_d_names)


```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("ggsci::amber_material")
```

## One spatial dta example 

```{r}
vegetation <- read_sf("doc.kml") %>% 
  select(Name) %>% 
  clean_names()

ggplot(data = vegetation) +
  geom_sf(aes(fill = name), color = NA) +
  theme_minimal() +
  scale_fill_paletteer_d("khroma::land") +
  labs(title = "Jornada Basin LTER Vegetation",
       caption = "Source: Jornada LTER") 


```

```{r}
ggsave(filename = "my_awesome_map.jpg", width = 8, height = 5)
```

